NMRlipids III: Lipid-cholesterol interactions in atomistic resolution molecular dynamics simulations

### 2019-05-02 MANUSCRIPT/manuscript.tex
Add author
Add density results and update form factor figure
Add fittness results

@@

@@

 \begin{figure}[]
  \centering
  \includegraphics[width=8cm]{../FIGS/FormFactors.eps}
  \caption{\label{FormFactors}
    Form factors from simulations and experiments.
  }

  \todo{Form factor calculation method should be double checked.}

  \todo{Experimental form factor amplitudes are not scaled to match with simulations, as done usually}

  \todo{Not all experimental and simulation data is here.}

>>>>

\author{Markus Miettinen}
\affiliation{MPI}

@@

\begin{figure*}[]
  \centering
  \includegraphics[width=17.2cm]{../FIGS/OrderParametersCHOLfitness.eps}
  \caption{\label{OrderParametersCHOL}
    Difference between order parameters from simulations and experiments for acyl chains of  1-palmitoyl-2-oleoylphosphatidylcholine (POPC).
  }
\end{figure*}

@@

 \begin{figure}[]
  \centering
  \includegraphics[width=8cm]{../FIGS/FormFactors.eps}
  \caption{\label{FormFactors}
    Form factors from simulations and experiments.
  }
  \todo{Form factor calculation method should be double checked.}
  \todo{Experimental form factor amplitudes are not scaled to match with simulations, as done usually}
  \todo{Not all experimental and simulation data is here.}
\end{figure}

 \begin{figure}[]
  \centering
  \includegraphics[width=8cm]{../FIGS/FFfitness.eps}
  \caption{\label{FormFactorsFITNESS}
    Fitness of form factors between simulations and experiments.
  }
 \end{figure}

  \begin{figure}[]
  \centering
  \includegraphics[width=8cm]{../FIGS/densitiesEXTREMES.eps}
  \caption{\label{densities}
    Density profiles from simulations and experiments.
  }
\end{figure}
